Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-05-10 manuscript/manuscript.tex
Fixed exponential density test figure caption

\begin{figure*}
\centering
\includegraphics[width=\linewidth]{figures/exponential-delta.pdf}
\caption{
    Density functions used in the model comparison and the differences 
    between the gravitational fields generated by the numerical model 
    and the analytical solution for (a) a thin spherical shell of 1km 
    of thickness and (b) a thick spherical shell of 35km of thickness, 
    both with the exponential density defined on equation 
    \ref{eq:density-exp}.
    A few values of the constant $b$ were used in order to test the 
    numerical model for different density variations.
    The computations were performed on the big grid described in 
    Table \ref{tab:grids}, with fixed values of the distance-size ratio 
    $D$ obtained for in the linear density case ($D=1, 2, 8$ for the 
    potential, gradient components and tensor components, respectively)
    and different values of the $\delta$ ratio.
    If the difference is less than 0.1\%, we consider that the model 
    has achieved an acceptable accuracy for the corresponding value of 
    $D$.
    }
\label{fig:delta-exponential}
\end{figure*}

>>>>

\begin{figure*}
\centering
\includegraphics[width=\linewidth]{figures/exponential-delta.pdf}
\caption{
    Density functions used in the $\delta$ ratio determination and the 
    differences between the gravitational fields generated by the 
    numerical model and the analytical solution for a thin and a thick 
    spherical shell of 1km adn 35km of thickness, respectively, both 
    with the exponential density defined on equation 
    \ref{eq:density-exp}.
    A few values of the constant $b$ were used in order to test the 
    numerical model for different density variations.
    The computations were performed on the big grid described in 
    Table \ref{tab:grids}, with fixed values of the distance-size ratio 
    $D$ obtained for in the linear density case ($D=1, 2, 8$ for the 
    potential, gradient components and tensor components, respectively)
    and different values of the $\delta$ ratio.
    If the difference is less than 0.1\%, we consider that the model 
    has achieved an acceptable accuracy for the corresponding value of 
    $\delta$.
    }
\label{fig:delta-exponential}
\end{figure*}
